\documentclass[11pt]{article}

\usepackage[papersize={8.5in,11in},margin=1in]{geometry}
\usepackage[final,stretch=10,shrink=10]{microtype} % default of stretch=shrink=20 is a little too much
\usepackage{amsmath,amsfonts,amsxtra,amssymb}
\usepackage{url}
\usepackage{bm}
\usepackage[sort&compress]{natbib}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage[normalem]{ulem}
\usepackage{xcolor}
\usepackage[shadow,prependcaption,textsize=small]{todonotes}

\usepackage{comment}

\definecolor{bluey}{rgb}{0.0,0.2,0.5}
\newcommand{\mycomment}[1]{\textit{\color{bluey}#1}}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}
\newcommand{\green}[1]{\textcolor{green}{#1}}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\magenta}[1]{\textcolor{magenta}{#1}}
\newcommand{\argmin}{\operatorname{arg}\min}
\newcommand{\R}{\mathbb{R}}

\newcommand{\fa}{\mathfrak{a}}
\newcommand{\fb}{\mathfrak{b}}
\newcommand{\fab}{\fa\fb}
\newcommand{\fba}{\fb\fa}
\newcommand{\muab}{\mu_{\fa\fb}}
\newcommand{\nuab}{\nu_{\fa\fb}}
\newcommand{\ha}{H^{\fa}}
\newcommand{\hb}{H^{\fb}}

%\definecolor{rev1}{HTML}{cb270f}
%\definecolor{rev2}{HTML}{1c8235}


\begin{document}

\addtocounter{page}{-1}
\thispagestyle{empty}

\hfill
\begin{flushright}
Correspondence to: \\
Tristan van Leeuwen\\
\texttt{t.van.leeuwen@cwi.nl}\\
\end{flushright}

\vspace{1em}
\hfill\today
\ \\
\ \\
\ \\
\noindent Dear Editor,\ \\

\noindent  Thank you for forwarding the reviews of our article
titled \emph{An Analysis of Constraint-Relaxation in PDE-Based Inverse Problems} which was submitted to \textit{Inverse Problems}. \ \\

\noindent  We are appreciative of the reviews made by the referees and  the further suggestions.\ \\

\noindent Attached to this letter is a response to the third referee. Corresponding changes have been colored in blue in the new revision. \ \\

\noindent We would like to resubmit for consideration the enclosed revision, and we look forward to hearing from the Editor. \ \\

\noindent  Sincerely, \ \\

\noindent  Tristan van Leeuwen and Yunan Yang



\clearpage


\centerline{\textbf{{\large Response to the Third Referee}}}
\ \\
We thank the third referee for the comprehensive review and many suggestions that significantly improved the manuscript. Please see below for our response to the comments. 

\begin{itemize}
    \item[R3.1] \mycomment{The first sentence of the abstract should be removed. Perhaps it should be combined with the second " Many inverse problems are naturally formulated as a PDE-constrained optimization problem."  Also, perhaps instead of saying we provide an in-depth analysis , say "we analyze a relaxed formulation...}

We thank the referee for the suggestion. We have updated the abstract based on the comments.


\item[R3.2] \mycomment{I am not sure the introduction needs separate subsections. (the last subsection is just one paragraph)}

We have removed the title of the subsections in the Introduction.


\item[R3.3] \mycomment{Is there a better section title for section 2?}

We renamed it to "Main results".

\end{itemize}


\end{document}